OpenMPIR

### 2017-10-06 paper.tex
add middle initial
minor rewording of that memory model section

\author{Stephen Olivier}
\affiliation{\institution{Center for Computing Research \\ Sandia National Laboratories}}
\email{slolivi@sandia.gov}

@@

The surprising fact that program behavior wasn't changed significantly is worth
discussing. We surmise that it is likely due to the semantics of variables
borrowed from the Cilk codegen and their relation to the OpenMP specification
of semantics. In particular, \emph{OpenMP specifies a relaxed memory model
for shared variables}, in which writes by one thread need only be visible at
to other threads at explicit or implicit flushes. 
This results in the Cilk implementation of only writing
to a shared variable at the end of a parallel section being a valid
implementation of OpenMP's specification. In contrast, existing OpenMP
implementations sometimes write shared variables to memory on every write access. This is a
potential for performance discrepancy because of differing 
implementation behavior.
%Stephen:This topic is not discuessed later, but was touched on before -- moved?
%and we will return to it when discussing
%performance on the Barcelona OpenMP task suite. 
There is of course the fact
that technically, by copying the value of variables back to the surrounding
context even for \texttt{private} variables, one isn't following the
specification. We surmise that in practice this hasn't had an effect because
\texttt{private} variables are often used for input parameters in the 
progams or for performance rather than their semantic properties.
Also, \texttt{firstprivate} is the default data-sharing attribute for tasks.

>>>>

\author{Stephen L. Olivier}
\affiliation{\institution{Center for Computing Research \\ Sandia National Laboratories}}
\email{slolivi@sandia.gov}

@@

The surprising fact that program behavior wasn't changed significantly is worth
discussing. We surmise that it is likely due to the semantics of variables
borrowed from the Cilk codegen and their relation to the OpenMP specification
of semantics. In particular, \emph{OpenMP specifies a relaxed memory model
for shared variables}, in which writes by one thread need only be visible at
to other threads at explicit or implicit flushes. 
This results in the Cilk implementation of only writing
to a shared variable at the end of a parallel section being a valid
implementation of OpenMP's specification. In contrast, existing OpenMP
implementations sometimes write shared variables to memory on every write access. This is a
potential for performance discrepancy because of differing 
implementation behavior.
%Stephen:This topic is not discuessed later, but was touched on before -- moved?
%and we will return to it when discussing
%performance on the Barcelona OpenMP task suite. 
There is of course the fact
that technically, by copying the value of variables back to the surrounding
context even for \texttt{private} variables, one isn't following the
specification. We surmise that in practice this hasn't had an effect because
\texttt{private} variables are often used for inputs to calculations that are 
not accessed after the tasks complete, 
or for performance rather than their semantic properties.
Also, \texttt{firstprivate} is the default data-sharing attribute for tasks.
